---
title: "Investigation of ToothGrowth Dataset"
subtitle: Course Project for **Statistical Inference** classes on **Coursera**
author: "Igor Goltsov <riversy@gmail.com>"
output: pdf_document
---

This work is my own investigation of *ToothGrowth* dataset that describes effect of Vitamin C on tooth growth in Guinea Pigs. There are two methods of Vitamin C suppliement: Orange Juice and Ascorbic Acid. And there are three doses of Vitamin C applied to pigs: 0.5, 1 and 2 miligrams. 

## 1. Exporatory Analisys

First of all I woul like to load dataset and have a brief look onto data.

```{r}
library(datasets)
data("ToothGrowth")
head(ToothGrowth)
```

On a brief look we have 6 groups of data about length of tooth. I would like to create additional column *group* what will help me to compare these groups. I will use **dplyr** package to do that. 

```{r}
library(dplyr)
tooth_growth_grouped <- 
    mutate(ToothGrowth, group = paste(supp, dose, sep = "-")) %>%
    select(len, group)

head(tooth_growth_grouped)
```

We have grouped data and I would like to visualize the density of values for each of group. 

```{r}
library(ggplot2)
ggplot(
        tooth_growth_grouped, 
        aes(x = factor(group), y = len, fill = factor(group))
    ) +
    geom_violin(col = "black", size = 2)
```

Let's assume that the greater length of tooth is better for us. We may see the influence of Ascorbic Acid have a greatet effect to lenght of tooth then the use Oragnge Juice. And we also may see that the greater value of Vitamin C in Ascorbic Acid has greater influence then less value of Vitamin C.

## 2. Compare Ascorbic Acid quantity influence

I would like to compare two groups *VC-0.5* and *VC-2* as more outstanding groups to the minimum and to the maximum of lengths. Suppose 2mg of Vitamin C that injected with Ascorbic Acid has greater effect for tooth lenght then 0.5mg of Vitamin C that was injected same way. I will use T-Test to check this hypothesis.

```{r}
vc0.5 <- tooth_growth_grouped$len[tooth_growth_grouped$group == "VC-0.5"]
vc2 <- tooth_growth_grouped$len[tooth_growth_grouped$group == "VC-2"]

t.test(vc2, vc0.5, var.equal = FALSE, paired = FALSE)
```

As we may see, T-Test confidence interval is placed above zero so it's mean our hypothesis is true. We may also may see that **mean** of *VC-2* group is much greater then **mean** of *VC-0.5* group that also confirm our suggestion.  

